Named Entity Recognition on HTML as a web data extraction subtask

### 2018-09-21 tex/article.tex
Nice tables.

\DeclareMathOperator*{\argmax}{arg\,max\,}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l| }
      \hline
      Data file & Documents & Sentences & Tokens & Names \\
      \hline
      Training    & 92 & 28958 & 124984 & 6382 \\
      Validation  & 28 & 9117  & 39748  & 2258 \\
      Test        & 25 & 5790  & 26995  & 1949 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Number of HTML pages, sentences and tokens in each data file}
  \label{tab:dataset}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Feature & Description \\
      \hline
      1  & Unaccented lowercase token \\
      2  & Exact gazetteer match \\
      3  & Partial gazetteer match \\
      4  & Log name gazetteer count\\
      5  & Log word gazetteer count\\
      6  & Email \\
      7  & Number \\
      8  & Honorific \\
      9  & URL \\
      10 & Is capitalized \\
      11 & Is a punctuation sign \\
      12 & HTML tag + parent \\
      13 & CSS class \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Features present in the bla dataset}
  \label{tab:features}
\end{table}

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
names. Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in a word corpus obtained through a random crawl in university websites.
Features 6 to 11 represent a simple regular expression match to an email, number, 
honorific, URL, capitalization and punctuation sign.

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Model & Description \\
      \hline
      hmm-1         & Regular HMM \\
      hmm-2         & HMM with $ k=2 $ \\
      hmm-3         & HMM with $ k=3 $ \\
      crf           & Linear chain conditional random fields \\
      lstm-crf      & LSTM-CRF model \cite{Huang2015} \\
      lstm-crf-cnn  & LSTM-CRF with CNN character representations \cite{Ma2016} \\
      lstm-crf-lstm & LSTM-CRF with LSTM character representations \cite{Lample2016} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Model descriptions}
  \label{tab:models}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l|l|l| }
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1	      & 0.6965 & 0.5749 & 0.6299 & 0.6263 & 0.4431 & 0.5190 \\
      hmm-2	      & 0.7047 & 0.6286 & 0.6645 & 0.6480 & 0.5222 & 0.5783 \\
      hmm-3	      & 0.6127 & 0.6141 & 0.6134 & 0.5471 & 0.4634 & 0.5018 \\
      crf	      & 0.7237 & 0.6650 & 0.6931 & 0.6734 & 0.5879 & 0.6278 \\
      lstm-crf        & 0.8607 & 0.8848 & 0.8726 & 0.8546 & 0.8294 & 0.8418 \\
      lstm-crf-cnn    & 0.9221 & 0.9206 & 0.9214 & 0.9030 & 0.8283 & 0.8640 \\
      lstm-crf-lstm   & 0.9129 & 0.9441 & 0.9282 & 0.8906 & 0.8807 & 0.8856 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the complete dataset}
  \label{tab:experiment1}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l|l|l| }
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1+F	      & 0.6061 & 0.7282 & 0.6616 & 0.7106 & 0.7633 & 0.7360 \\
      hmm-2+F	      & 0.6279 & 0.7550 & 0.6856 & 0.7521 & 0.7810 & 0.7663 \\
      hmm-3+F	      & 0.6573 & 0.7819 & 0.7142 & 0.7523 & 0.7795 & 0.7657 \\
      hmm-1+F+ST      & 0.7032 & 0.9077 & 0.7925 & 0.7522 & 0.8663 & 0.8052 \\
      hmm-2+F+ST      & 0.7321 & 0.9172 & 0.8143 & 0.7737 & 0.8789 & 0.8230 \\
      hmm-3+F+ST      & 0.7551 & 0.9172 & 0.8283 & 0.7961 & 0.8534 & 0.8237 \\
      crf+F	      & 0.8982 & 0.9128 & 0.9054 & 0.8812 & 0.8298 & 0.8547 \\
      lstm-crf+F      & 0.9378 & 0.9441 & 0.9409 & 0.8959 & 0.8807 & 0.8883 \\
      lstm-crf-cnn+F  & 0.8998 & 0.9799 & 0.9382 & 0.8910 & 0.9295 & 0.9098 \\
      lstm-crf-lstm+F & 0.9495 & 0.9569 & 0.9532 & 0.9163 & 0.8888 & 0.9023 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the complete dataset}
  \label{tab:experiment1f}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|}
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-2           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-3           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      crf             & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-cnn    & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-lstm   & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the small dataset}
  \label{tab:experiment2}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|}
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-2+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-3+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-1+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-2+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-3+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      crf+F           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf+F      & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-cnn+F  & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-lstm+F & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the small dataset}
  \label{tab:experiment2f}
\end{table}

>>>>

\DeclareMathOperator*{\argmax}{arg\,max\,}
\renewcommand{\arraystretch}{1.2}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lllll }
      \toprule
      Data file & Documents & Sentences & Tokens & Names \\
      \midrule
      Training    & 85 & 24728 & 110269 & 5822 \\  
      Validation  & 30 & 8743  & 36757  & 1788 \\
      Test        & 30 & 10399 & 44795  & 2708 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Number of HTML pages, sentences and tokens in each data file}
  \label{tab:dataset}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ ll }
      \toprule
      Feature & Description \\
      \midrule
      1  & Unaccented lowercase token \\
      2  & Exact gazetteer match \\
      3  & Partial gazetteer match \\
      4  & Log name gazetteer count\\
      5  & Log word gazetteer count\\
      6  & Email \\
      7  & Number \\
      8  & Honorific \\
      9  & URL \\
      10 & Is capitalized \\
      11 & Is a punctuation sign \\
      12 & HTML tag + parent \\
      13 & CSS class \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Features used in the NER on HTML dataset}
  \label{tab:features}
\end{table}

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lllll }
      \toprule
      Data file & Precision & Recall & F1 & Correct names \\
      \midrule
      Training   & 0.7316 & 0.2303 & 0.3504 & 1341 from 5822 \\ 
      Validation & 0.8474 & 0.2858 & 0.4274 & 511 from 1788 \\ 
      Test       & 0.8717 & 0.3287 & 0.4773 & 890 from 2708 \\ 
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Gazetteer coverage in each data file}
  \label{tab:gazetteer}
\end{table}

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
names. Table \ref{tab:gazetteer} shows the precision, recall and F1 score obtained with an
exact gazetteer matching strategy in each data file as a baseline.
Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in a word corpus obtained through a random crawl in university websites.
Features 6 to 11 represent a simple regular expression match to an email, number, 
honorific, URL, capitalization and punctuation sign.

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ ll }
      \toprule
      Model & Description \\
      \midrule
      hmm-1         & Regular HMM \\
      hmm-2         & HMM with $ k=2 $ \\
      hmm-3         & HMM with $ k=3 $ \\
      crf           & Linear chain conditional random fields \\
      lstm-crf      & LSTM-CRF model \cite{Huang2015} \\
      lstm-crf-cnn  & LSTM-CRF with CNN character representations \cite{Ma2016} \\
      lstm-crf-lstm & LSTM-CRF with LSTM character representations \cite{Lample2016} \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Model descriptions}
  \label{tab:models}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lllllll }
      \toprule
      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test} \\
                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1}
                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} \\
      \midrule
      hmm-1	    & 0.6965 & 0.5749 & 0.6299 & 0.6263 & 0.4431 & 0.5190 \\
      hmm-2	    & 0.7047 & 0.6286 & 0.6645 & 0.6480 & 0.5222 & 0.5783 \\
      hmm-3	    & 0.6127 & 0.6141 & 0.6134 & 0.5471 & 0.4634 & 0.5018 \\
      crf	    & 0.7173 & 0.6683 & 0.6920 & 0.6671 & 0.5868 & 0.6244 \\
      lstm-crf	    & 0.8484 & 0.9044 & 0.8755 & 0.8358 & 0.8497 & 0.8427 \\
      lstm-crf-cnn  & 0.9058 & 0.9575 & 0.9309 & 0.8779 & 0.8737 & 0.8758 \\
      lstm-crf-lstm & 0.9134 & 0.9435 & 0.9282 & 0.8920 & 0.8815 & 0.8867 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the complete dataset}
  \label{tab:experiment1}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lllllll }
      \toprule
      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test} \\
                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1}
                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} \\
      \midrule
      hmm-1+F	      & 0.6061 & 0.7282 & 0.6616 & 0.7106 & 0.7633 & 0.7360 \\
      hmm-2+F	      & 0.6279 & 0.7550 & 0.6856 & 0.7521 & 0.7810 & 0.7663 \\
      hmm-3+F	      & 0.6573 & 0.7819 & 0.7142 & 0.7523 & 0.7795 & 0.7657 \\
      hmm-1+F+ST      & 0.7032 & 0.9077 & 0.7925 & 0.7522 & 0.8663 & 0.8052 \\
      hmm-2+F+ST      & 0.7321 & 0.9172 & 0.8143 & 0.7737 & 0.8789 & 0.8230 \\
      hmm-3+F+ST      & 0.7551 & 0.9172 & 0.8283 & 0.7961 & 0.8534 & 0.8237 \\
      crf+F	      & 0.9024 & 0.9049 & 0.9037 & 0.8751 & 0.8227 & 0.8481 \\
      lstm-crf+F      & 0.9430 & 0.9530 & 0.9480 & 0.8998 & 0.8527 & 0.8756 \\
      lstm-crf-cnn+F  & 0.9244 & 0.9715 & 0.9474 & 0.9017 & 0.8973 & 0.8995 \\
      lstm-crf-lstm+F & 0.9465 & 0.9692 & 0.9577 & 0.9108 & 0.8715 & 0.8907 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the complete dataset}
  \label{tab:experiment1f}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lllllll }
      \toprule
      \multirow{2}{*}{Model} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} & \multicolumn{2}{c}{F1} \\
                             & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}} \\
      \midrule
      hmm-1	      & 0.2856 & 0.1127 & 0.1623 & 0.0810 & 0.2036 & 0.0892 \\
      hmm-2	      & 0.3436 & 0.1134 & 0.2060 & 0.1058 & 0.2483 & 0.0997 \\
      hmm-3	      & 0.2707 & 0.0955 & 0.2163 & 0.0927 & 0.2316 & 0.0793 \\
      crf	      & 0.6249 & 0.0433 & 0.5272 & 0.0348 & 0.5711 & 0.0301 \\
      lstm-crf	      & 0.6982 & 0.0495 & 0.6538 & 0.0532 & 0.6751 & 0.0499 \\
      lstm-crf-cnn    & 0.7906 & 0.0557 & 0.7431 & 0.0687 & 0.7652 & 0.0572 \\
      lstm-crf-lstm   & 0.7935 & 0.0345 & 0.7360 & 0.0424 & 0.7626 & 0.0237 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the small dataset}
  \label{tab:experiment2}
\end{table}

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{lllllll}
      \toprule
      \multirow{2}{*}{Model} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} & \multicolumn{2}{c}{F1} \\
                             & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}} \\
      \midrule
      hmm-1+F	      & 0.6205 & 0.0927 & 0.6402 & 0.0717 & 0.6290 & 0.0774 \\
      hmm-2+F	      & 0.5999 & 0.0879 & 0.6527 & 0.0389 & 0.6229 & 0.0595 \\
      hmm-3+F	      & 0.5712 & 0.0957 & 0.6258 & 0.0494 & 0.5954 & 0.0722 \\
      hmm-1+F+ST      & 0.6536 & 0.0886 & 0.7579 & 0.1118 & 0.7012 & 0.0963 \\
      hmm-2+F+ST      & 0.7044 & 0.0726 & 0.7810 & 0.1039 & 0.7397 & 0.0834 \\
      hmm-3+F+ST      & 0.6619 & 0.0722 & 0.7174 & 0.0892 & 0.6879 & 0.0777 \\
      crf+F	      & 0.8419 & 0.0326 & 0.7530 & 0.0823 & 0.7933 & 0.0541 \\
      lstm-crf+F      & 0.8376 & 0.0225 & 0.7838 & 0.0518 & 0.8093 & 0.0345 \\
      lstm-crf-cnn+F  & 0.8542 & 0.0336 & 0.7820 & 0.0767 & 0.8149 & 0.0478 \\
      lstm-crf-lstm+F & 0.8554 & 0.0219 & 0.8013 & 0.0825 & 0.8255 & 0.0478 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the small dataset}
  \label{tab:experiment2f}
\end{table}
